---
title       : Developing Data Products Project
subtitle    : August 2014
author      : harric17
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Introduction

<p>My project Shiny app is hosted at <a href="http://harric17.shinyapps.io/project/">this website</a>.
</p>

<p>This is a simple app that uses "melanom" dataset form the ISwR package in R.  The app gets Kaplan-Meier survival parameter estimates based on the stratifications specified.  As long as the user knows how to operate a pulldown menu they should have no problem using this app.</p>

--- .class #id 

## Data Set

<p>More information on the "melanom" dataset can be found in the  <a href="http://cran.r-project.org/web/packages/ISwR/ISwR.pdf">ISwR package documention</a>.  Specifically see page 18.
</p>

To save you the trouble here are the variables:
```{r}
# install.packages("ISwR")
library("ISwR")
names(melanom)
```

And here are some summaries of the variables of interest:
```{r}
table(melanom$sex)
table(melanom$status)
summary(melanom$days)
```
---

